\documentclass{tccv}
\makeatletter
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\makeatother
\usepackage[english]{babel}

\begin{document}

\part{Matthew Nathan Heler}

\section{Work Experience}

\begin{eventlist}

\item{March 2019 -- Current}
	 {Red Hat}
	 {Senior Storage Consultant}
	 
Working within the Emerging Technology Group. My role as a consultant is to leverage Ceph, Gluster and emerging platform technologies for Red Hat customers across the industry.

\item{October 2018 -- March 2019}
	 {Insight Global}
	 {Software Developer (Contract)}
	 
Assigned to the AT\&T account to improve Ceph support, resiliency, and capabilities for the Airship project. Worked on the development of Helm charts to automate the deployment, upgrade and day to day operations of Ceph on top of Kubernetes.

\item{November 2014 -- September 2018}
	 {Rackspace}
	 {Private Cloud Architect \\ Private Cloud Engineer III \\ Storage Engineer IV}

Originally a lead storage engineer at Rackspace, then moved into the Private Cloud team to support OpenStack. Specialized in Ceph, Storage and OpenStack.

\item{July 2013 -- October 2014}
     {SalesForce.com}
     {Senior Backup Engineer}

Deployment and support engineer on the Netbackup team. Lead on DPA and OpsCenter implementations.

\item{October 2012 -- June 2013}
     {Putnam Investments}
     {Senior Technical Expert}

Primary engineer for Putnam's Backup enviroment, which consisted of Avamar, Netbackup and Datadomain appliances.

\item{February 2012 -- September 2012}
     {Dell Services}
     {Senior Advisor}

Assigned to the account managing Harvard Pilgrim Healthcare's infrastructure. Architect and lead engineer on the backup team, responsible for the Netbackup, DataDomain appliances and Tape solutions. Documented standardized operational procedures and run books for the operations and datacenter teams.

\item{July 2011 -- February 2012 \\ (Canada) April 2010 -- June 2011}
     {Nokia Corporation}
     {Senior Storage Administrator \\ Deployment Specialist}

Originally hired onto the deployment infrastructure team responsible for the mobile messaging platform in Montreal, Canada. Moved to a new position within a team based in Burlington, MA that was repsonsible for the all of the enterprise storage (VNX, Clariion, Celerra, Centera, and Atmos) within Nokia's global datacenters.

\item{(Canada) May 2008 -- February 2010}
    {Ubisoft Entertainment}
    {Storage and Backup Administrator}

Operations lead on Netbackup, Enterprise Vault, and StorageTrek libraries. Documented the global backup procedures for Ubisoft's worldwide datacenters.
\end{eventlist}

\section{Contact Information}

\personal
    {2303 Shiloh Dr \newline Austin, TX 78745}
    {+1 (617) 372 1066}
    {matthew.heler@hotmail.com}

\section{Certifications}

\begin{yearlist}

\item{Redhat}
	{RHCA, RHCE, RHCVA, RHCSA}
	{OpenStack, OpenShift, Gluster, Ceph, Cloudforms, Virtualization}

\item{EMC}
	{EMCIE, EMCPE, EMCISA}
	{DataDomain, Avamar, XtremIO, VNX}
	
\item{ITIL}
	{FOUNDATION v3}

\end{yearlist}

\section{Technology Skills}

\begin{factlist}

\item{Good level}
     {OpenStack, Ceph, Swift, Ansible, Redhat, Bash, Puppet, DataDomain, Netbackup, SAN (EMC VNX, VMAX, XtremIO, SolidFire, PureStorage), NAS (NetApp), Git}

\item{Intermediate}
     {MySQL, Postgres, NetApp, AWS, Redis, Docker, Kubernetes, Helm, Gluster, Avamar}

\item{Basic level}
     {\LaTeX, MongoDB, Oracle}

\end{factlist}


\end{document}
